---
title: "lab_7 script"
author: "Deanna Strayer, Alex Newson, Sabreen NoorAli, Tony Daza, Seulbi Lee"
date: "11/2/2022"
output: html_document
bibliography: references.bib
csl: apa-annotated-bibliography.csl
---

```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 6.5, fig.height = 8)
```

```{r, echo = FALSE}
library(tidyverse)
library(here)
library(rio)
library(janitor)
library(ggplot2)
library(dplyr)

star <- import(here("data","star.csv"), setclass="tbl_df") %>%
  clean_names()

```

#Question 3:  
**Table of Summary Statistics Examining Math and Reading scores by sex and Free/reduced Price Lunch Status**  
```{r}
star_table <- star %>%
  select("sex", "frl", "tmathss", "treadss") %>%
  group_by(sex, frl) %>%
  summarise(math_mean = mean(tmathss), 
            math_sd = sd(tmathss), 
            rdg_mean = mean(treadss), 
            rdg_sd = sd(treadss))
star_table %>%
  mutate(across(where(is.numeric), round, 2))
```

The table above shows the mean and standard deviation of math and reading scores for boys and girls mediated by free and reduced price lunch status.  

Girls without Free/Reduced price lunch had the highest math and reading scores while boys without Free/Reduced price lunch scored higher than both boys and girls *with* Free/Reduced Price lunch.  

The mean math score for boys *with* Free/Reduced price lunch was **469.87** compared to boys with *paid lunch* who had an average math score of **492.85**

The trend continued for girl where the mean math score for girls *with* Free/Reduced price lunch was **477.51** compared to girls with *paid lunch* who had an average math score of **501.21**

Furthermore the trend was identical for reading scores suggesting that Free/Reduced Price Lunch status mediates the relationship between math and reading scores for boys and girls.  

Further analysis will have to be conducted to evaluate the magnitude of the effect for the Free/Reduced Price Lunch variable on math and reading scores, but that is outside the scope of this assignment.  


# Question 4:  
**Examining Teacher Experience as a predictor of Math Score mediated by Free/Reduced Price Lunch status**  

```{r}
ggplot(star, aes(x = totexp, y = tmathss )) + 
  geom_point(color = "grey", alpha = 0.5) + 
  geom_smooth(aes(color = frl), method = lm, se = TRUE) +
  theme_minimal() + 
  labs(x = "Teacher Experience (Years)", 
       y = "Total Math Scale Score",
       title = "Relation between Teacher Experience and Math Score",
       subtitle = "Separate Regression lines displayed by free/reduced price lunch status", 
       color = "Lunch status") +
  theme(legend.position = "bottom")
```

This is r-markdown document has [@vanderheyden_is_2018] as a reference.

This is r-markdown document has [@polikoff_instructional_2010] as a reference.

This is r-markdown document has Naumann et al.'s article [-@naumann_sensitivity_2019] as a reference.

This is r-markdown document has Stockard et al.'s article [-@stockard_effectiveness_2018] as a reference.


# References
